---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# todotxt

[![Travis build status](https://travis-ci.org/MHenderson/todotxt.svg?branch=master)](https://travis-ci.org/MHenderson/todotxt)
[![Coverage status](https://codecov.io/gh/MHenderson/todotxt/branch/master/graph/badge.svg)](https://codecov.io/github/MHenderson/todotxt?branch=master)

[Todo.txt](http://todotxt.org/) is a
[standard](https://github.com/todotxt/todo.txt) for text-based todo lists.
The goal of this package is to parse todo.txt files like
[this one](http://todotxt.org/todo.txt) into tibbles.

Most of the work of parsing todo.txt files in **todotxt** is done by the
Python [todotxtio](https://github.com/EpocDotFr/todotxtio) package.

We also expose other functionality from the todotxtio Python package for
updating todo lists to support users in building todo.txt based applications.

## Installation

You can install todotxt from github with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MHenderson/todotxt")
```

```{r, echo = FALSE}
reticulate::use_python("/usr/bin/python3")
```

```{r}
library(httr)
library(magrittr)
library(todotxt)

GET("http://todotxt.org/todo.txt") %>%
  content("text") %>%
  todotxt()
```
